Woman in Workplace ^[Code and data are available at:https://github.com/Faustine123/Newspapers-in-Times-of-Low-Advertising-Revenues]

### 2023-04-21 Output/Paper/Paper.qmd
model

```{r}

@@

# Print the summary of the regression model
summary(model)

#table

library(texreg)

>>>>

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}

@@

model2 <- lm_robust(share_of_university_and_college_presidents_who_are_women_in_percents ~ year, data = unipresidents_rawdata)

model3 <- lm_robust(Value ~ TIME, data = edu_rawdata)

model4 <- lm_robust(Value ~ TIME, data = wagegap_rawdata)

# Create model summary table
library(modelsummary)
modelsummary(list(model, model2, model3, model4),
             fmt = 2,
             title = "Model Summary of",
             output = 'markdown')
```
